---
title: "Mini HW 4-2: More work on functions"
author: "Your Name"
date: "Today's date"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

**Due Thursday, November 6 through Github**

In this next assignment, you will continue working on creating functions in `R`. next assignment is to practice creating functions in `R`.

For reference, here are functions to calculate a 95% confidence interval for a mean and a 95% confidence interval for a difference in means, as done on Mini HW 4-1.
```{r}
mean_ci <- function(x) {
  xbar <- mean(x, na.rm=TRUE)
  n <- sum(!is.na(x))
  se <- sd(x, na.rm=TRUE) / sqrt(n)
  xbar + c(-2, 2) * se
}

two_mean_ci <- function(x, y) {
  xbar <- mean(x, na.rm=TRUE)
  ybar <- mean(y, na.rm=TRUE)
  
  estimate <- xbar - ybar
  
  n_x <- sum(!is.na(x))
  n_y <- sum(!is.na(y))
  s_x <- sd(x, na.rm=TRUE)
  s_y <- sd(y, na.rm=TRUE)
  
  se <- sqrt(s_x^2/n_x + s_y^2/n_y)
             
  estimate + c(-2, 2) * se
}
```

1. Using the code in the two functions above, write a function called `means_ci()` that takes the arguments listed below and returns either a 95% confidence interval for a single mean or a 95% confidence interval for the difference in means depending on those arguments.  I've given default values for these arguments as well.

* `x` (no default value)
* `y` (default value is `NULL` which corresponds to `one.mean` option for the `type` argument)
* `type` (default value is `one.mean`, other value is `two.means`)
* `...` (to be able to pass the `na.rm` option through to the mean/sd functions as needed)

Consider including a a way to check whether the vectors of `x` and `y` are numeric and thus such a confidence interval is appropriate.

```{r}
# put your code for your function here




# check your code on the following:
set.seed(12345)
x <- rnorm(100)
y <- runif(75)

means_ci(x)   # should get [1] 0.02225103 0.46814336 

means_ci(x, y, type="two.means")   # should get [1] -0.53662437 -0.06933551 

x2 <- c(x, NA)
y2 <- c(y, NA)
means_ci(x2, y2, type="two.means")  # should get [1] NA NA
means_ci(x2, y2, type="two.means", na.rm=TRUE)   # should get [1] -0.53662437 -0.06933551 
```


2. Update your function from #1 to include an argument called `conf.level` that allows you to specify a confidence level of either `0.90`, `0.95`, or `0.99`. 

**Hint:** The approximate multiplier for 90% confidence interval is 1.65.  The approximate multiplier for a 99% confidence interval is 2.6.

```{r}
# put your code for your function here



# do a couple of checks on your code



```


___

When you are finished with your assignment, knit your file and submit through Github. To do so, follow the steps below.  (If your document didn't successfully knit, please reach out to me over email at `phbiostats@jhu.edu` so I can help you trouble-shoot the issue.)

* First you need to **commit** the changes you've made to the document.  Click the colorful Git button at the top of the RStudio window and select "Commit" from the menu.
* In the window that opens, **stage** your changes by clicking the check box next to the `Mini4-2.Rmd` file.
* In the "Commit message" box, type a short description of what changes you've made, something like: `Completed assignment`
* Click the "Commit" button on the bottom right.
* You'll see a window that will tell you about the changes that you've made.  Click "Close" to close the window.  You've successfully committed! You can close this commit window now.
* After committing, you must **push** your changes to the repository on Github.  Do this by clicking the colorful Git button again and select "Push Branch".  
* Again, you'll see a window open that tells you your changes have been pushed!
* If you want, you can look at your repository on [Github.com](https://github.com/) and should be able to see your changes there!  
* You've successfully submitted your assignment :)


